What We Eval in the Shadows

### 2021-09-09 paper/main.tex
Fix in 6

The R language was intended to be extensible. The combination of lazy
evaluation, \k{substitute}, and \k{eval} are some of the tools given to
developers to this end. To understand \emph{why} developers use \eval, we
manually inspected the top 117 sites, which contribute to 90\% of the calls in
the corpus. We present examples from nine classes from this batch. The
classification is not exhaustive as we only study a fraction from the
\PkgEvalCallSites call sites in our corpus, and many uses of \eval do not fit
in a specific category. Instead, the goal is to demonstrate the wide variety of
uses to which \eval is put to use. At the high level, the usage can be grouped
into two groups: one contains patterns that aim to provide better
API for R users and the other focuses on simplifying implementation.

>>>>

The R language was intended to be extensible. The combination of lazy
evaluation, \k{substitute}, and \k{eval} are some of the tools given to
developers to this end. To understand \emph{why} developers use \eval, we
manually inspected the top 117 sites, which contribute to 90\% of the calls in
the corpus. We present examples from nine classes from this batch. The
classification is not exhaustive as we only study a fraction from the
\PkgEvalCallSites call sites in our corpus, and many uses of \eval do not fit
in a specific category. Instead, the goal is to demonstrate the wide variety of
uses to which \eval is put to use. At the high level, the usage can be grouped
into two groups: one contains patterns that aim to provide better
API and the other focuses on simplifying implementation.
